High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 overall.tex
fix a minor placement error.

    \item REVIEWER 2: What are the reasons for the low efficiency of PanDA
    Broker? Why are only 30\% of backfill slots useable, if they are
    basically uncontested?

@@

    \item REVIEWER 2: Given an expected increase in resource need of 10-100,
    how is the capacity of 4\% WLCG significant? How does this relate to the
    manpower required to develop and maintain a custom solution per HPC site?
    How many TITAN resources are actually available to HEP, given the use by
    other domains? The magnitude of capacities presented as available is in
    major contrast to the requirements sketched in the introduction.\jhanote{MT to address this via a few sentences in Section IV.}

>>>>

    \item REVIEWER 2: What are the reasons for the low efficiency of PanDA
    Broker? Why are only 30\% of backfill slots useable, if they are basically
    uncontested? \jhanote{MT to address this via a few sentences in Section
    IV.}

@@

    \item REVIEWER 2: Given an expected increase in resource need of 10-100,
    how is the capacity of 4\% WLCG significant? How does this relate to the
    manpower required to develop and maintain a custom solution per HPC site?
    How many TITAN resources are actually available to HEP, given the use by
    other domains? The magnitude of capacities presented as available is in
    major contrast to the requirements sketched in the introduction.
